---
title: 'Supplementaries for Chapter 5'
author: "Mitra Barzine"
date: "2020"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
    number_sections: true
    theme: united
    highlight: pygments
    smart: true
    css: ../styles.css
    includes:
      after_body: ../footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r initalisation}
suppressPackageStartupMessages(library(barzinePhdR))
Pastelpalette7 <- c("#e6b7bf","#98d4e4","#ddbea5","#aec1e0","#d3e2bc","#d1bbdf","#a8cfbf")
Intensepalette7<-c("#a10096","#ffb853","#014695","#f4003d","#02c3be","#493100","#ffaec2")
revPastelpalette7 <- c("#a8cfbf","#e6b7bf","#98d4e4","#ddbea5","#aec1e0","#d3e2bc","#d1bbdf")
otherPal7<-c("#F9DFC5","#D46658","#EBC4C0","#a8cfbf","#e6b7bf","#98d4e4","#DF3534")
otherPal7<-c(alpha("tomato3",0.7),alpha("tan1",0.7),alpha("coral4",0.7),"#72AB59","#6460B8","#CC6AB7","#993366")
```

# An overall fragmented and disparate universe to explore

## Shared and unique tissues across the three proteomic datasets {.tabset}
### Venn diagram 
```{r DistribShareUniqueTissueProt}
cutler.top3<-eval(barzinePhdData::cutler.top3)
kuster.top3<-eval(barzinePhdData::kuster.top3)
pandey.top3<-eval(barzinePhdData::pandey.top3)
TissueCol<-eval(barzinePhdData::TissueCol_62)
datasetCol<-eval(barzinePhdData::datasetCol)

DrawVenn(a=cutler.top3,b=kuster.top3,c=pandey.top3,
         names=c('Cutler','Kuster','Pandey'),
         cols=datasetCol[c('Cutler','Kuster','Pandey')],
         type='colnames',
         cat.cex=rep(2,3),
         cat.dist=c(0.07,0.07,0.09),
         cex=rep(2,7))
```


### UpsteR plot
```{r }
InputList3ProtDF<-list(Cutler=colnames(cutler.top3),Kuster=colnames(kuster.top3),
                Pandey=colnames(pandey.top3))
UpSetR::upset(UpSetR::fromList(InputList3ProtDF),order.by='degree',
      sets.x.label = "Tissues number per Study",
      point.size = 3, line.size = 2, 
      text.scale = c(1.1, 0.95, 1.15, 1, 1.6, 0.90),
      mb.ratio = c(0.60, 0.40)
      )
```


## Overlap of proteins across the commun tissues {.tabset}

```{r commonTissues}
commonT<-Intersect(colnames(cutler.top3),colnames(kuster.top3),colnames(pandey.top3))
cutler.top3.commonT<-strip(cutler.top3[,commonT])
kuster.top3.commonT<-strip(kuster.top3[,commonT])
pandey.top3.commonT<-strip(pandey.top3[,commonT])
```

### Venn diagram
```{r vennDiagCommonTissue}
DrawVenn(fontfamily='Linux Libertine',
     a=cutler.top3.commonT,
     b=kuster.top3.commonT,
     c=pandey.top3.commonT,
     names=names(datasetCol[6:8]),
     cols=datasetCol[6:8],
     type='rownames',
     cat.cex=rep(2,3),
     cat.dist=c(0.07,0.07,0.05),
     cex=rep(2,7))
```

### UpsetR plot
```{r overlapUpsPrtop3.commonTT}
InputList3ProtDFCommProt<-list(Cutler=rownames(cutler.top3.commonT),
                 Kuster=rownames(kuster.top3.commonT),
                Pandey=rownames(pandey.top3.commonT))
UpSetR::upset(UpSetR::fromList(InputList3ProtDFCommProt),order.by='degree',
      sets.x.label = "Protein number for \n the four shared tissue per study",
      point.size = 3, line.size = 2, 
      text.scale = c(1.1, 0.95, 1.15, 1, 1.6, 0.90),
      mb.ratio = c(0.60, 0.40)
      )
```


## Breakdown by tissue {.tabset}

### Heart {.tabset}
#### UpsetR plot
```{r overlapProtHeart}
InputListHeart<-list(Cutler=rownames(cutler.top3.commonT[cutler.top3.commonT$Heart>0,]),
                 Kuster=rownames(kuster.top3.commonT[kuster.top3.commonT$Heart>0,]),
                 Pandey=rownames(pandey.top3.commonT[pandey.top3.commonT$Heart>0,]))

UpSetR::upset(UpSetR::fromList(InputListHeart),order.by='degree',
      sets.x.label = "Protein number identified for\nHeart in each study",
      point.size = 3, line.size = 2, 
      text.scale = c(1.1, 0.95, 1.15, 1, 1.6, 0.90),
      mb.ratio = c(0.60, 0.40)
      )
```

#### Venn diagram
```{r overlapVenProtHeart}
DrawVenn(fontfamily='Linux Libertine',
     a=rownames(cutler.top3.commonT[cutler.top3.commonT$Heart>0,]),
     b=rownames(kuster.top3.commonT[kuster.top3.commonT$Heart>0,]),
     c=rownames(pandey.top3.commonT[pandey.top3.commonT$Heart>0,]),
     names=names(datasetCol[6:8]),
     cols=datasetCol[6:8],
     type='vec',
     cat.cex=rep(2,3),
     cat.dist=c(0.07,0.07,0.05),
     cex=rep(2,7))
```


### Lung {.tabset}
#### UpsetR plot
```{r overlapProtLung}
InputListLung<-list(Cutler=rownames(cutler.top3.commonT[cutler.top3.commonT$Lung>0,]),
                 Kuster=rownames(kuster.top3.commonT[kuster.top3.commonT$Lung>0,]),
                 Pandey=rownames(pandey.top3.commonT[pandey.top3.commonT$Lung>0,]))


UpSetR::upset(UpSetR::fromList(InputListLung),order.by='degree',
      sets.x.label = "Protein number identified for\nLung in each study",
      point.size = 3, line.size = 2, 
      text.scale = c(1.1, 0.95, 1.15, 1, 1.6, 0.90),
      mb.ratio = c(0.60, 0.40)
      )

```

#### Venn diagram
```{r overlapVenProtLung}
DrawVenn(fontfamily='Linux Libertine',
     a=rownames(cutler.top3.commonT[cutler.top3.commonT$Lung>0,]),
     b=rownames(kuster.top3.commonT[kuster.top3.commonT$Lung>0,]),
     c=rownames(pandey.top3.commonT[pandey.top3.commonT$Lung>0,]),
     names=names(datasetCol[6:8]),
     cols=datasetCol[6:8],
     type='vec',
     cat.cex=rep(2,3),
     cat.dist=c(0.07,0.07,0.05),
     cex=rep(2,7))
```

### Ovary {.tabset}
#### UpsetR plot
```{r overlapProtOvary}
InputListOvary<-list(Cutler=rownames(cutler.top3.commonT[cutler.top3.commonT$Ovary>0,]),
                 Kuster=rownames(kuster.top3.commonT[kuster.top3.commonT$Ovary>0,]),
                 Pandey=rownames(pandey.top3.commonT[pandey.top3.commonT$Ovary>0,]))

UpSetR::upset(UpSetR::fromList(InputListOvary),order.by='degree',
      sets.x.label = "Protein number identified for\nOvary in each study",
      point.size = 3, line.size = 2, 
      text.scale = c(1.1, 0.95, 1.15, 1, 1.6, 0.90),
      mb.ratio = c(0.60, 0.40)
      )
```

#### Venn diagram
```{r overlapVenProtOvary}
DrawVenn(fontfamily='Linux Libertine',
     a=rownames(cutler.top3.commonT[cutler.top3.commonT$Ovary>0,]),
     b=rownames(kuster.top3.commonT[kuster.top3.commonT$Ovary>0,]),
     c=rownames(pandey.top3.commonT[pandey.top3.commonT$Ovary>0,]),
     names=names(datasetCol[6:8]),
     cols=datasetCol[6:8],
     type='vec',
     cat.cex=rep(2,3),
     cat.dist=c(0.07,0.07,0.05),
     cex=rep(2,7))
```


### Pancreas {.tabset}
#### UpsetR plot
```{r overlapProtPancreas}
InputListPancreas<-list(Cutler=rownames(cutler.top3.commonT[cutler.top3.commonT$Pancreas>0,]),
                 Kuster=rownames(kuster.top3.commonT[kuster.top3.commonT$Pancreas>0,]),
                 Pandey=rownames(pandey.top3.commonT[pandey.top3.commonT$Pancreas>0,]))

UpSetR::upset(UpSetR::fromList(InputListPancreas),order.by='degree',
      sets.x.label = "Protein number identified for\nPancreas in each study",
      point.size = 3, line.size = 2, 
      text.scale = c(1.1, 0.95, 1.15, 1, 1.6, 0.90),
      mb.ratio = c(0.60, 0.40)
      )
```

#### Venn diagram
```{r overlapVenProtPancreas}
DrawVenn(fontfamily='Linux Libertine',
     a=rownames(cutler.top3.commonT[cutler.top3.commonT$Pancreas>0,]),
     b=rownames(kuster.top3.commonT[kuster.top3.commonT$Pancreas>0,]),
     c=rownames(pandey.top3.commonT[pandey.top3.commonT$Pancreas>0,]),
     names=names(datasetCol[6:8]),
     cols=datasetCol[6:8],
     type='vec',
     cat.cex=rep(2,3),
     cat.dist=c(0.07,0.07,0.05),
     cex=rep(2,7))
```


## For information: comparison Kuster and Pandey only {.tabset}
### Tissue
```{r TissueOverlapProtKusterPandey}
DrawVenn(fontfamily='Linux Libertine',
     a=kuster.top3,
     b=pandey.top3,
     names=names(datasetCol[7:8]),
     cols=datasetCol[7:8],
     type='colnames',
     cat.cex=rep(2,2),
     cat.dist=c(-0.05,-0.05),
     cex=rep(2,3))
```

### Number of proteins for the commun tissues
```{r common14T}
comProt.14T<-intersect(colnames(kuster.top3),colnames(pandey.top3))
kuster.oT14<-strip(kuster.top3[,comProt.14T])
pandey.oT14<-strip(pandey.top3[,comProt.14T])
```

```{r overlapProt14T2D}
DrawVenn(fontfamily='Linux Libertine',
     a=kuster.oT14,
     b=pandey.oT14,
     names=names(datasetCol[7:8]),
     cols=datasetCol[7:8],
     type='rownames',
     cat.cex=rep(2,2),
     cex=rep(1.8,3))
```

### Breakdown for the other 10 tissues {.tabset}
```{r Venndiag14T_helper}
extractTissue<-function(DF,tissue,threshold=0,type='gt'){
  toReturn<-setNames(DF[,tissue],rownames(DF))
  switch(type,
         'gt'={toReturn<-toReturn[toReturn>threshold]},
         'ge'={toReturn<-toReturn[toReturn%>=%threshold]},
         'eq'={toReturn<-toReturn[toReturn==threshold]},
         'lt'={toReturn<-toReturn[toReturn<threshold]},
         'le'={toReturn<-toReturn[toReturn%<=%threshold]}
  )
  return(toReturn)
}
```

```{r results='asis'}
tmp<-lapply(setdiff(comProt.14T,commonT),function(x){
  cat(paste('#####',x,'\n'))
  
  DrawVenn(fontfamily='Linux Libertine',
             a=extractTissue(kuster.top3,x),
             b=extractTissue(pandey.top3,x),
             names=names(datasetCol[7:8]),
             cols=datasetCol[7:8],
             type='namedV',
             cat.cex=rep(2,2),
             cat.dist=c(-0.01,-0.01),
             cex=rep(1.8,3))
  cat("\n\n\n")
  
})
```

# MS proteomic data has high detection variability
## Number of identified proteins in each of the four common tissues for the three proteomic data. {.tabset}

Proteins found in more than one dataset are most likely true (in red, light and darker green or purple — the most validated ones in red as they are found in all three datasets).

### Figure
```{r barplotProt4T, fig.height=4, fig.width=9.5}
protTable<-barplotCommonGenesUnique3D(cutler.top3,
                                    kuster.top3,
                                    pandey.top3,
                                    name=c('Cutler','Kuster','Pandey'),
                                    out='DF',
                                    colorpalette = otherPal7,
                                    ylab='Protein count',
                                    baseSize = 18, baseFamily = 'Linux Libertine')
```

### Table
```{r barplotData}
protTable$Name<-barzinePhdData::gene.mapID[protTable$ID]
DT::datatable(protTable,rownames = FALSE,
              caption = "Proteins observed in the four common tissues of Cutler, Kuster and Pandey",
              extensions = 'Buttons', 
              options = list(
                dom = 'Bfrtip',
                buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
                ))
```

## Distribution of the proteins per tissue across the three datasets
```{r ProteinsPerTissuePerdataset, fig.width=5.5, fig.height=3.5, results="asis"}
cat('### Cutler')
tmp1<-nbGenesPerCond.unique(cutler.top3, 
                          legend.title = 'Proteins within\ntissue/cell',
                          ylab= "Number of proteins",
                          Y=c(0,6100),
                          legendPosition='bottom',
                          print=FALSE,
                          out='plot',
                          thm=theme(axis.title.x=element_blank()))+ggtitle("Cutler")
cat('### Kuster')
tmp2<-nbGenesPerCond.unique(kuster.top3, 
                          legend.title = 'Proteins within\ntissue/cell',
                          ylab= "Number of proteins",
                          Y=c(0,6100),
                          legendPosition='bottom',
                          print=FALSE,
                          out='plot',
                          thm=theme(axis.title.x=element_blank()))+ggtitle("Kuster")

cat('### Pandey')
tmp3<-nbGenesPerCond.unique(pandey.top3, 
                          legend.title = 'Proteins within\ntissue/cell',
                          ylab= "Number of proteins",
                          Y=c(0,6100),
                          legendPosition='bottom',
                          print=FALSE,
                          out='plot',
                          thm=theme(axis.title.x=element_blank()))+ggtitle("Pandey")
```


# PPKM quantification {.tabset}
## Shared and unique tissues across the two proteomic datasets 
```{r DistribShareUniqueTissueProtPPKM}
kuster.ppkm<-eval(barzinePhdData::kuster.ppkm)
pandey.ppkm<-eval(barzinePhdData::pandey.ppkm)

DrawVenn(a=kuster.ppkm,b=pandey.ppkm,
         names=c('Kuster','Pandey'),
         cols=datasetCol[c('Kuster','Pandey')],
         type='colnames',
         cat.cex=rep(2,2),
         cex=rep(1.8,3))
```

## Shared and unique proteins across the two proteomic datasets 
```{r DistribShareUniqueProtPPKM}
comProt.ppkm<-intersect(colnames(kuster.ppkm),colnames(pandey.ppkm))
kuster.oT14ppkm<-strip(kuster.top3[,comProt.ppkm])
pandey.oT14ppkm<-strip(pandey.top3[,comProt.ppkm])

DrawVenn(fontfamily='Linux Libertine',
     a=kuster.oT14ppkm,
     b=pandey.oT14ppkm,
     names=names(datasetCol[7:8]),
     cols=datasetCol[7:8],
     type='rownames',
     cat.cex=rep(2,2),
     cex=rep(1.8,3))
```


# Protein Supersets {.tabset}

## Protein found in every tissue of every dataset (ubiquitous) {.tabset}

### TOP3 
```{r ubiquitousProtein}
ubiquitousPandey<-ubi.strict(pandey.top3)
ubiquitousKuster<-ubi.strict(kuster.top3)
ubiquitousCutler<-ubi.strict(cutler.top3)

ubiquitousProtein<-Intersect(ubiquitousPandey,ubiquitousKuster)
ubiquitousProteinCutler<-Intersect(ubiquitousPandey,ubiquitousKuster,ubiquitousCutler)
```

#### Common to the three proteomic datasets
```{r nameID3D}
DT::datatable(nameID(ubiquitousProteinCutler,out='DF'),
              rownames = FALSE,
              caption = 'Ubiquitous proteins common to Cutler, Kuster and Pandey (TOP3)',
              colnames = c('Gene id'='ensembl_gene_id','Gene name' = 'hgnc_symbol'),
              extensions = 'Buttons', 
              options = list(
                dom = 'Bfrtip',
                buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
                ))
```

#### Ubiquitous and common to Kuster Lab and Pandey Lab data only
```{r nameID}
DT::datatable(nameID(ubiquitousProtein,'DF'),
              rownames = FALSE,
              caption = 'Ubiquitous proteins common to Kuster and Pandey (TOP3)',
              colnames = c('Gene id'='ensembl_gene_id','Gene name' = 'hgnc_symbol'),
              extensions = 'Buttons', 
              options = list(
                dom = 'Bfrtip',
                buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
                ))
```

### PPKM
Ubiquitous and common to Kuster Lab and Pandey Lab data only
```{r ubiquitousProteinPPKM}
ubiquitousPandey.ppkm<-ubi.strict(pandey.ppkm)
ubiquitousKuster.ppkm<-ubi.strict(kuster.ppkm)
ubiquitousPPKM<-intersect(ubiquitousPandey.ppkm,ubiquitousKuster.ppkm)

DT::datatable(nameID(ubiquitousPPKM,out='DF'),
              rownames = FALSE, 
              caption = 'Ubiquitous proteins common to Kuster and Pandey (PPKM)',
              colnames = c('Gene id'='ensembl_gene_id','Gene name' = 'hgnc_symbol'),
              extensions = 'Buttons', 
              options = list(
                dom = 'Bfrtip',
                buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
                ))
```


## Protein unique (TS) {.tabset}
```{r TissueUniqueHelpers}
splitTissueSpe<-function(vec,verbose=FALSE){
  cond<-unique(vec)
  resList<-lapply(setNames(cond,cond), 
                  function(x){
                    if(verbose) print(paste(x,':',length(vec[vec==x])))
                    names(vec[vec==x])
                  })
  return(resList)  
}

prepDTname<-function(theRes,prefix="#####"){
    tmp<-lapply(names(theRes), function(x){
      cat(paste(prefix,x,'\n'))
      cat(knitr::knit_print(
      DT::datatable(
        data.frame(id=theRes[[x]],name=barzinePhdData::gene.mapID[theRes[[x]]]),
        rownames = FALSE, colnames = c('Ensembl id' = 'id','Gene name' = 'name'),
        extensions = 'Buttons', 
        options = list(
          dom = 'Bfrtip',
          buttons = c('copy', 'csv', 'excel', 'pdf', 'print') 
      ))))
   cat("\n\n\n")
    })
}
```

### TOP 3 {.tabset}

#### Cutler {.tabset .tabset-pills}
```{r TSprotCutler,results="asis"}
cutler.unique<-protSpe(cutler.top3)
cutler.unique<-cutler.unique[!is.na(cutler.unique)]#1644 spe prot in total
cutler.uniqueSplitted<-splitTissueSpe(cutler.unique)
prepDTname(cutler.uniqueSplitted)
```

#### Kuster {.tabset .tabset-pills}
```{r TSprotKuster,results="asis"}
kuster.unique<-protSpe(kuster.top3)
kuster.unique<-kuster.unique[!is.na(kuster.unique)]#1071 spe prot in total
kuster.uniqueSplitted<-splitTissueSpe(kuster.unique)
prepDTname(kuster.uniqueSplitted)
```

#### Pandey {.tabset .tabset-pills}
```{r TSprotPandey,results="asis"}
pandey.unique<-protSpe(pandey.top3)
pandey.unique<-pandey.unique[!is.na(pandey.unique)]#1491 spe prot in total
pandey.uniqueSplitted<-splitTissueSpe(pandey.unique)
prepDTname(pandey.uniqueSplitted)
```

#### Consistent TS across the three proteomic datasets
```{r TSprot}
heartUnique<-Intersect(unlist(cutler.uniqueSplitted$Heart),
                       unlist(pandey.uniqueSplitted$Heart),
                       unlist(kuster.uniqueSplitted$Heart))
lungUnique<-Intersect(unlist(cutler.uniqueSplitted$Lung),
                      unlist(pandey.uniqueSplitted$Lung),
                      unlist(kuster.uniqueSplitted$Lung))
ovaryUnique<-Intersect(unlist(cutler.uniqueSplitted$Ovary),
                       unlist(pandey.uniqueSplitted$Ovary),
                       unlist(kuster.uniqueSplitted$Ovary))
pancreasUnique<-Intersect(unlist(cutler.uniqueSplitted$Pancreas),
                          unlist(pandey.uniqueSplitted$Pancreas),
                          unlist(kuster.uniqueSplitted$Pancreas))
```

Number of TS protein common between Cutler Lab, Kuster Lab and Pandey Lab data for:

* Heart: `r length(heartUnique)`
* Lung: `r length(lungUnique)`
* Ovary: `r length(ovaryUnique)`
* Pancreas: `r length(pancreasUnique)`

```{r TSprot2D}
CommUniquePandeyKuster<-lapply(setNames(comProt.14T,comProt.14T), 
                               function(x){
                                # print(paste(x,':',
                                #             length(Intersect(unlist(kuster.uniqueSplitted[x]),
                                #                              unlist(pandey.uniqueSplitted[x])))))
                                 return(Intersect(unlist(kuster.uniqueSplitted[x]),unlist(pandey.uniqueSplitted[x])))
                               })
```


List of TS protein common between Kuster Lab and Pandey Lab data:
```{r}
pander::pander(CommUniquePandeyKuster)
```


### PPKM

List of TS protein common between Kuster Lab and Pandey Lab data (PPKM):
```{r TSprotPPKM,results="asis"}
pandey.ppkm.unique<-protSpe(pandey.ppkm)
kuster.ppkm.unique<-protSpe(kuster.ppkm)

kuster.ppkm.unique<-kuster.ppkm.unique[!is.na(kuster.ppkm.unique)]#1987 spe prot in total
kuster.ppkm.uniqueSplitted<-splitTissueSpe(kuster.ppkm.unique)

pandey.ppkm.unique<-pandey.ppkm.unique[!is.na(pandey.ppkm.unique)]#2640 spe prot in total
pandey.ppkm.uniqueSplitted<-splitTissueSpe(pandey.ppkm.unique)


CommUniquePandeyKuster.ppkm<-lapply(setNames(comProt.ppkm,comProt.ppkm), 
                               function(x){
                                 #print(paste(x,':',
                                 #           length(Intersect(unlist(kuster.ppkm.uniqueSplitted[x]),
                                 #                            unlist(pandey.ppkm.uniqueSplitted[x])))))
                                 return(Intersect(unlist(kuster.ppkm.uniqueSplitted[x]),
                                                  unlist(pandey.ppkm.uniqueSplitted[x])))
                               })
pander::pander(CommUniquePandeyKuster.ppkm)
```



### Common between TOP3 and PPKM
```{r resultsTSprot}
Unique.PPKM.top3<-lapply(setNames(comProt.14T,comProt.14T), 
                               function(x){
                                 #print(paste(x,':',
                                 #           length(Intersect(unlist(CommUniquePandeyKuster.ppkm[x]),
                                 #                            unlist(CommUniquePandeyKuster[x])))))
                                 return(Intersect(unlist(CommUniquePandeyKuster.ppkm[x]),
                                                  unlist(CommUniquePandeyKuster[x])))
                               })
pander::pander(Unique.PPKM.top3)
```

# Technical variability prevails over biological signal: intrastudy correlations of different tissues are globally stronger than same-tissue interstudy correlations.

## Correlation {.tabset}
```{r commonProt}
comRowProt.T4<-Intersect(rownames(cutler.top3.commonT),
                         rownames(kuster.top3.commonT),
                         rownames(pandey.top3.commonT))
cutler.T4p<-cutler.top3.commonT[comRowProt.T4,]
kuster.T4p<-kuster.top3.commonT[comRowProt.T4,]
pandey.T4p<-pandey.top3.commonT[comRowProt.T4,]
protT4<-cbind(suffix(cutler.T4p,'Cutler)',sep=' ('),
              suffix(kuster.T4p,'Kuster)',sep=' ('),
              suffix(pandey.T4p,'Pandey)',sep=' ('))


comRowProt.T14<-intersect(rownames(kuster.oT14),rownames(pandey.oT14))
kuster.T14p<-kuster.oT14[comRowProt.T14,]
pandey.T14p<-pandey.oT14[comRowProt.T14,]
protT14<-cbind(suffix(kuster.T14p,'Kuster)',sep=' ('),
              suffix(pandey.T14p,'Pandey)',sep=' ('))

```

```{r commonPnoMito}
protT4_noMito<-excludeGenes(protT4,barzinePhdData::g.mitoch)
protT4_noMitoNoCont<-excludeGenes(protT4_noMito,ubiquitousProteinCutler)
protT14_noMito<-excludeGenes(protT14,barzinePhdData::g.mitoch)
```

### For the 3 datasets - 4 tissues
```{r CorrelationHeatmap}
mHeatmapTC(protT4_noMito,
        method='spearman',
        RowsideMode ='extractSpace',ColsideMode = 'extractSpace',
        common.cond=common.T4,
        TissueCol=TissueCol,
        datasetCol=datasetCol,
        margins=c(8,10),key.title = 'Spearman Correlation',
        cexRow = 1.2,cexCol = 1.2)

mHeatmapTC(protT4_noMitoNoCont,
        method='spearman',
        RowsideMode ='extractSpace',ColsideMode = 'extractSpace',
        common.cond=common.T4,
        TissueCol=TissueCol,
        datasetCol=datasetCol,
        margins=c(8,10),key.title = 'Spearman Correlation',
        cexRow = 1.2,cexCol = 1.2)

mHeatmapTC(protT4_noMito,
        method='pearson',
        RowsideMode ='extractSpace',ColsideMode = 'extractSpace',
        common.cond=common.T4,
        TissueCol=TissueCol,
        datasetCol=datasetCol,
        margins=c(8,10),key.title = 'Pearson Correlation',
        cexRow = 1.2,cexCol = 1.2)

mHeatmapTC(protT4_noMitoNoCont,
        method='pearson',
        RowsideMode ='extractSpace',ColsideMode = 'extractSpace',
        common.cond=common.T4,
        TissueCol=TissueCol,
        datasetCol=datasetCol,
        margins=c(8,10),key.title = 'Pearson Correlation',
        cexRow = 1.2,cexCol = 1.2)
```

### For the 2 datasets - 14 tissues 
```{r CorrelationHeatmap14T2D}
mHeatmapTC(protT14_noMito,
        method='spearman',
        RowsideMode ='extractSpace',ColsideMode = 'extractSpace2',
        common.cond=common.T14,
        TissueCol=TissueCol,
        datasetCol=datasetCol,
        margins=c(8,11),key.title = 'Spearman Correlation',
        cexRow = 1.2,cexCol = 1.2,
        baseFont = 'Linux Libertine')

mHeatmapTC(protT14_noMito,
        method='pearson',
        RowsideMode ='extractSpace',ColsideMode = 'extractSpace2',
        common.cond=common.T14,
        TissueCol=TissueCol,
        datasetCol=datasetCol,
        margins=c(8,11),key.title = 'Pearson Correlation',
        cexRow = 1.2,cexCol = 1.2,
        baseFont = "Linux Libertine")

```

### Scatterplots 

```{r 3Dprotscatter}
scatplot.log2(protT4_noMito,x="Heart (Cutler)",y="Heart (Pandey)", title="Pandey ~ Cutler:  Heart",xlabs='Cutler',ylab='Pandey',dealWithSpace = TRUE,max=-4,min=-20,xcor=-10,ycor=-5,family='Linux Libertine')

scatplot.log2(protT4_noMito,x="Heart (Kuster)",y="Heart (Pandey)", title="Pandey ~ Kuster:  Heart",xlabs='Kuster',ylab='Pandey',dealWithSpace = TRUE,max=-3,min=-20,xcor=-10,ycor=-5,family='Linux Libertine')


scatplot.log2(protT4_noMito,x="Lung (Cutler)",y="Lung (Pandey)", title="Pandey ~ Cutler:  Lung",xlabs='Cutler',ylab='Pandey',dealWithSpace = TRUE,max=-4,min=-20,xcor=-10,ycor=-5,family='Linux Libertine')

scatplot.log2(protT4_noMito,x="Lung (Cutler)",y="Pancreas (Cutler)", title="Cutler: Pancreas ~ Lung",xlabs='Lung',ylab='Pancreas',dealWithSpace = TRUE,max=-3,min=-20,xcor=-10,ycor=-3.8,family='Linux Libertine')

scatplot.log2(protT4_noMito,x="Lung (Pandey)",y="Pancreas (Pandey)", title="Pandey: Pancreas ~ Lung",xlabs='Lung',ylab='Pancreas',dealWithSpace = TRUE,max=-3,min=-20,xcor=-10,ycor=-4,family='Linux Libertine')

scatplot.log2(protT4_noMito,x="Ovary (Cutler)",y="Pancreas (Cutler)", title="Cutler: Pancreas ~ Ovary",xlabs='Ovary',ylab='Pancreas',dealWithSpace = TRUE,max=-3,min=-20,xcor=-10,ycor=-4,family='Linux Libertine')

scatplot.log2(protT4_noMito,x="Ovary (Pandey)",y="Pancreas (Pandey)", title="Pandey: Pancreas ~ Ovary",xlabs='Ovary',ylab='Pancreas',dealWithSpace = TRUE,max=-3,min=-20,xcor=-10,ycor=-3.8,family='Linux Libertine')
```

```{r more2DprotScatter}
scatplot.log2(protT14_noMito,x="Heart (Kuster)",y="Heart (Pandey)", title="Pandey ~ Kuster:  Heart",xlabs='Kuster',ylab='Pandey',dealWithSpace = TRUE,max=-3,min=-20.2,xcor=-11,ycor=-3.5,family='Linux Libertine')

scatplot.log2(protT14_noMito,x="Lung (Kuster)",y="Lung (Pandey)", title="Pandey ~ Kuster:  Lung",xlabs='Kuster',ylab='Pandey',dealWithSpace = TRUE,max=-3,min=-20.2,xcor=-11,ycor=-3.5,family='Linux Libertine')

scatplot.log2(protT14_noMito,x="Kidney (Kuster)",y="Kidney (Pandey)", title="Pandey ~ Kuster:  Kidney",xlabs='Kuster',ylab='Pandey',dealWithSpace = TRUE,max=-3,min=-20.2,xcor=-11,ycor=-3.5,family='Linux Libertine')

scatplot.log2(protT14_noMito,x="Placenta (Kuster)",y="Placenta (Pandey)", title="Pandey ~ Kuster:  Placenta",xlabs='Kuster',ylab='Pandey',dealWithSpace = TRUE,max=-3,min=-20.2,xcor=-11,ycor=-3.5,family='Linux Libertine')

scatplot.log2(protT14_noMito,x="Liver (Kuster)",y="Liver (Pandey)", title="Pandey ~ Kuster:  Liver",xlabs='Kuster',ylab='Pandey',dealWithSpace = TRUE,max=-3,min=-20.2,xcor=-11,ycor=-3.5,family='Linux Libertine')

scatplot.log2(protT14_noMito,x="Adrenal (Kuster)",y="Adrenal (Pandey)", title="Pandey ~ Kuster:  Adrenal",xlabs='Kuster',ylab='Pandey',dealWithSpace = TRUE,max=-3,min=-20.2,xcor=-11,ycor=-3.5,family='Linux Libertine')

scatplot.log2(protT14_noMito,x="Gallbladder (Kuster)",y="Gallbladder (Pandey)", title="Pandey ~ Kuster:  Gallbladder",xlabs='Kuster',ylab='Pandey',dealWithSpace = TRUE,max=-3,min=-20.2,xcor=-11,ycor=-3.5,family='Linux Libertine')

scatplot.log2(protT14_noMito,x="Pancreas (Kuster)",y="Pancreas (Pandey)", title="Pandey ~ Kuster:  Pancreas",xlabs='Kuster',ylab='Pandey',dealWithSpace = TRUE,max=-3,min=-20.2,xcor=-11,ycor=-3.5,family='Linux Libertine')

scatplot.log2(protT14_noMito,x="Pancreas (Kuster)",y="Colon (Kuster)", title="Kuster: Colon ~ Pancreas",xlabs='Colon',ylab='Pancreas',dealWithSpace = TRUE,max=-3,min=-20.2,xcor=-11,ycor=-3.5,family='Linux Libertine')

scatplot.log2(protT14_noMito,x="Pancreas (Kuster)",y="Adrenal (Kuster)", title="Kuster:  Adrenal ~ Pancreas",xlabs='Kuster',ylab='Pandey',dealWithSpace = TRUE,max=-3,min=-20.2,xcor=-11,ycor=-3.5,family='Linux Libertine')

scatplot.log2(protT14_noMito,x="Pancreas (Kuster)",y="Adrenal (Pandey)", title="Pandey Adrenal ~ Kuster Pancreas",xlabs='Pancreas (Kuster)',ylab='Adrenal (Pandey)',dealWithSpace = TRUE,max=-3,min=-20.2,xcor=-11,ycor=-3.5,family='Linux Libertine')
```


## New quantification method
### Pandey data
#### Distribution barplots (per tissue)

```{r SameColumns}
colPandey<-intersect(colnames(pandey.top3),colnames(pandey.ppkm))
selectedTissues<-c("Testis", "Ovary", "Pancreas", "Prostate",
                   "Liver", "Colon", "Urinarybladder", "Adrenal", 
                   "Rectum","Gallbladder", "Kidney", "Placenta", 
                   "Lung", "Heart", "Oesophagus")
```

```{r firstquantification}
tm3<-nbGenesPerCond.unique(pandey.top3[,selectedTissues],
                           legend.title = 'Proteins within tissue/cell',
                           ylab= "Number of proteins",xlab='Tissue or Cell type')
```

```{r distributionPlotQ2} 
tm3b<-nbGenesPerCond.unique(pandey.ppkm[,selectedTissues],
                            legend.title = 'Proteins within tissue/cell',
                            ylab= "Number of proteins",xlab='Tissue or Cell type')
```


```{r compareQ1Q2b}
tm3b$variable<-factor(tm3b$variable,levels=levels(tm3$variable))

comp.q1q2<-rbind(data.frame(Quantification='Q1',tm3),
                 data.frame(Quantification='Q2',tm3b))

comp.q1q2$Color<-paste(comp.q1q2$Quantification,comp.q1q2$unique,sep='.')
comp.q1q2$Color<-as.factor(comp.q1q2$Color)
comp.q1q2$Color<-factor(comp.q1q2$Color, 
                        levels=c("Q1.Tissue/cell specific",
                                 "Q1.Unspecific to tissue or cell",
                                 "Q2.Tissue/cell specific",
                                 "Q2.Unspecific to tissue or cell"))

colnames(comp.q1q2)<-c("Quantification","ID", "Tissue", "value","unique","Color")

comp.q1q2$TM<-paste(comp.q1q2$Tissue,comp.q1q2$Quantification,sep=' - ')
comp.q1q2$TM<-as.factor(comp.q1q2$TM)
comp.q1q2$TM<-factor(comp.q1q2$TM, 
                      levels=c("Testis - Q1", "Testis - Q2",
                               "Ovary - Q1", "Ovary - Q2",
                               "Pancreas - Q1", "Pancreas - Q2",
                               "Prostate - Q1","Prostate - Q2",
                               "Liver - Q1", "Liver - Q2",
                               "Colon - Q1", "Colon - Q2",
                               "Urinarybladder - Q1", "Urinarybladder - Q2",
                               "Adrenal - Q1", "Adrenal - Q2",
                               "Rectum - Q1", "Rectum - Q2",
                               "Gallbladder - Q1","Gallbladder - Q2",
                               "Kidney - Q1", "Kidney - Q2",
                               "Placenta - Q1", "Placenta - Q2",
                               "Lung - Q1", "Lung - Q2",
                               "Heart - Q1", "Heart - Q2",
                               "Oesophagus - Q1", "Oesophagus - Q2"))
```

```{r creationPalette}
colorPaletteUnique<-setNames(c("#F8766D",  "#00BFC4", "#7CAE00","#C77CFF"),
                             c("Q1.Tissue/cell specific",
                               "Q1.Unspecific to tissue or cell",
                               "Q2.Tissue/cell specific",
                               "Q2.Unspecific to tissue or cell"))
```

```{r plot4}
p4 <- ggplot(comp.q1q2,aes(TM,y=..count..,fill=Color))+geom_bar()
p4 <- p4 + theme_bw(base_size=14)
p4 <- p4 + scale_fill_manual(values=colorPaletteUnique,drop=FALSE, 
                             labels=c("Unique in data quantified by the first method (Q1)",
                                      "Not unique in data quantified by the first method (Q1)",
                                      "Unique in data quantified by the new method (Q2)",
                                      "Not unique in data quantified by the new method (Q2)"))
p4 <- p4 + theme(axis.text.x=element_text(angle=45,hjust = 1),plot.title=element_text(hjust=0.5))+theme(legend.position = 'bottom',legend.title=element_text(size=10),legend.text = element_text(size=9.5))
p4 <- p4+xlab('Tissue')+guides(fill=guide_legend(title='Protein is',nrow=2))+ylab('Number of proteins')
p4
```


#### Density plots
```{r densityPlot}
density_plot<-function(DF,log2=TRUE,pseudocount=0,valueLab='Normalised Top3 PSM',
                       baseFont='Linux Libertine',condCol,fontSize=11,
                       publish=TRUE,title,
                       coord,xmin,xmax,ymin,ymax,removeLegend=FALSE,thm,
                       ylab){
  DF_lg<-reshape2::melt(DF)
  colnames(DF_lg)<-c('Tissue','value')
  
  if(log2) {
    if(pseudocount!=0)
      valueLab=paste0('Log2(',valueLab,' + ',pseudocount,')')
      else
      valueLab=paste0('Log2(',valueLab,')')
  }
  
  if(log2){
        p <- ggplot(DF_lg,aes(log2(value+pseudocount),fill=Tissue,colour=Tissue)) + geom_density(alpha=0.2)
      }else{
        p <- ggplot(DF_lg,aes(value,fill=Tissue,colour=Tissue)) + geom_density(alpha=0.2)
      }
      p <- p + xlab(valueLab)
      if(!missing(ylab)) p <- p + ylab(ylab)
      p <- p + scale_fill_manual(values=condCol)+ scale_colour_manual(values=condCol)
      p <- p + theme_bw(base_size = fontSize,base_family = baseFont)
      if(!missing(coord)) p <- p + coord_cartesian(xlim=c(xmin,xmax),ylim=c(ymin,ymax))
      if(publish) p<- p + theme_bw(base_family = baseFont)
      if(!missing(thm)) p<- p + thm
      p <- p+theme(plot.background = element_rect(fill = "transparent"))
      if(!missing(title)) p <- p + ggtitle(title)+theme(plot.title=element_text(hjust=0.5))
      if(removeLegend) p <- p+ theme(legend.position='none')
      return(p)
}
```
```{r densityplotQ1Q2}
densPlot1<-density_plot(pandey.top3[,selectedTissues],
                        condCol=TissueCol,removeLegend = TRUE,
                        title='First quantification (Q1)')
densPlot2<-density_plot(pandey.ppkm[,selectedTissues],
                        condCol=TissueCol,valueLab = 'PPKM', title='New quantification (Q2)')
```

```{r density}
gridExtra::grid.arrange(densPlot1,densPlot2,ncol=2,widths=c(1,1.5))
```

### New heatmap (For the 2 PPKM datasets - 14 tissues)
#### Preparation
```{r prepHeatmapPPKM}
common.T14.ppkm<-Intersect(colnames(pandey.ppkm),colnames(kuster.ppkm))
kuster.ppkm.T14<-strip(kuster.ppkm[,common.T14.ppkm])
pandey.ppkm.T14<-strip(pandey.ppkm[,common.T14.ppkm])

comRowProt.ppkm.14T<-intersect(rownames(pandey.ppkm.T14),rownames(kuster.ppkm.T14))

kuster.ppkm.T14<-kuster.ppkm.T14[comRowProt.ppkm.14T,]
pandey.ppkm.T14<-pandey.ppkm.T14[comRowProt.ppkm.14T,]
prot.ppkm.T14<-cbind(suffix(kuster.ppkm.T14,'Kuster)',sep=' ('),
               suffix(pandey.ppkm.T14,'Pandey)',sep=' ('))
prot.ppkm.T14_noMito<-excludeGenes(prot.ppkm.T14,barzinePhdData::g.mitoch)
```

#### Plots
```{r CorrelationHeatmap14T}
mHeatmapTC(prot.ppkm.T14_noMito,
        method='spearman',
        RowsideMode ='extractSpace',ColsideMode = 'extractSpace2',
        common.cond=common.T14.ppkm,
        TissueCol=TissueCol,
        datasetCol=datasetCol,
        margins=c(8,10),key.title = 'Spearman Correlation',
        cexRow = 1.2,cexCol = 1.2,
        baseFont = "Linux Libertine")

mHeatmapTC(prot.ppkm.T14_noMito,
        method='pearson',
        RowsideMode ='extractSpace',ColsideMode = 'extractSpace2',
        common.cond=common.T14.ppkm,
        TissueCol=TissueCol,
        datasetCol=datasetCol,
        margins=c(8,10),key.title = 'Pearson Correlation',
        cexRow = 1.2,cexCol = 1.2,
        baseFont = 'Linux Libertine')
```

## Presence of ORs ?

```{r querylist}
queryList<-c('OR6P1','OR1K1','OR6C75','OR2M4','OR9A2','OR52A5','OR11A1','OR1L1',
             'OR2A7','OR6N2','OR1A2','OR4E2','OR5K2','OR5C1','OR13C8','OR7C2',
             'OR51A4','OR4C13','OR4X2','OR56A3','OR2T11','OR5K4','OR5K1','OR1M1',
             'OR4A15','OR5K4','OR4P4','OR14I1','OR7A17','OR2W3','OR2T5','OR5I1',
             'OR9I1','OR3A1','OR5K4','OR2T33','OR6C1','OR51E2','OR51F1','OR1L4',
             'OR4A15','OR5T2','OR10G4',
             #from the picture on the paper:
             'OR10A2','OR10A5','OR10A7','OR10G4','OR10K1','OR10K2',
             'OR10Q1','OR10Z1','OR11A1','OR11G2','OR12D2','OR12D3',
             'OR13C3','OR13C4','OR13C8','OR13G1')
queryList<-unique(queryList)
```

```{r}
ensV=biomaRt::useMart("ensembl",dataset="hsapiens_gene_ensembl")
ORIDs<-biomaRt::getBM(attributes=c("ensembl_gene_id","external_gene_name"),
             mart=ensV,
             filters="external_gene_name",
             values=queryList)
rownames(ORIDs)<-ORIDs$ensembl_gene_id
DT::datatable(ORIDs)
ORIDens<-unique(ORIDs$ensembl_gene_id)
```

```{r simplequery}
length(intersect(rownames(ORIDs),rownames(cutler.top3)))
length(intersect(rownames(ORIDs),rownames(pandey.top3)))
length(intersect(rownames(ORIDs),rownames(kuster.top3)))
length(intersect(rownames(ORIDs),rownames(pandey.ppkm)))
intersect(rownames(ORIDs),rownames(pandey.ppkm))
length(intersect(rownames(ORIDs),rownames(kuster.ppkm)))
intersect(rownames(ORIDs),rownames(kuster.ppkm))
```

```{r heatmapPandeyQ1}
heatmap.2(log2(as.matrix(pandey.ppkm[intersect(rownames(ORIDs),rownames(pandey.ppkm)),]+1)),
          scale="none",
          key=T,keysize=1.5, density.info="none", trace="none",
          labRow =ORIDs[c("ENSG00000148136","ENSG00000170929", "ENSG00000258817"),"hgnc_symbol"],
          srtCol = 45,cexRow=1,
          margins = c(8,8),
          col=colorRampPalette(c('aliceblue','darkcyan'),bias=3),
          dendrogram = 'none',key.xlab = 'log2(PPKM+1)'#,
          )

pandey.ppkm[intersect(rownames(ORIDs),rownames(pandey.ppkm)),c('Kidney','Liver')]
```

##Other
### Scatter plot

```{r testScatplot}

protT4_noMito2<-protT4_noMito
colnames(protT4_noMito2)<-gsub('\\(','',colnames(protT4_noMito2))
colnames(protT4_noMito2)<-gsub('\\)','',colnames(protT4_noMito2))
colnames(protT4_noMito2)<-gsub(' ','',colnames(protT4_noMito2))

scatplot.log2(protT4_noMito2, x="HeartKuster",y="HeartPandey", xlabs= "Kuster",ylabs='Pandey',title="Heart: Pandey ~ Kuster",xmin=-20,ymin=-20,xmax=0,ymax=0)
```




