---
author: "Mitra Barzine"
date: "2020"
output: 
  html_document:
    code_download: true
    theme: united
    highlight: pygments
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: hide
    code_download: true
    number_sections: true
    df_print: paged
    css: ../styles.css
    includes:
      after_body: ../footer.html
---
---
title: `r dynTitle`
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(barzinePhdR))
flag4rChunks<-TRUE
flag4rChunks2D<-TRUE
flag4rChunks3D<-TRUE
op <- par(family = "Linux Libertine")

if(compDF=="3DF") flag4rChunks2D<-FALSE
if(compDF=="2DF") flag4rChunks3D<-FALSE
```

Notes:

* The analyses are built with [`barzinePhdR`](https://github.com/barzine/barzinePhdR), [`barzinePhdData`](https://github.com/barzine/barzinePhdData) packages and the additional packages: [`DT`](https://rstudio.github.io/DT/) and [`pander`](https://cran.r-project.org/web/packages/pander/index.html).  
* This report has been generated with the help of [`invocation.R`](invocation.R) and a [template](templateChap6-tissues.Rmd).

```{r otherFunctions}
pDF<-function(x,caption,signifnum=2,pageLength=15){
  DT::datatable( signif(x ,signifnum) ,
                caption=caption,
                extensions = c('Responsive','Buttons','ColReorder'),
                options = list(pageLength = pageLength,
                               dom='Blfrtip',
                               buttons = c('colvis','copy', 'csv', 'excel', 'pdf', 'print'),
                               colReorder = list(realtime = FALSE)))
}

makeTitle<-function(label,quantM,expCutoff){
  title<-label
  if(expCutoff){
    title<-paste(title,'( ≥',expCutoff)
  }else{
    title<-paste(title,'( > 0')
  }
  if(quantM=='top3'){
    title<-paste(title,'PSM (TOP3))')
  }else{
    title<-paste(title,toupper(quantM),')')
  }
}

geneID2df<-function(x,title){
  DT::datatable(
        data.frame(id=x,name=barzinePhdData::gene.mapID[x]),
        rownames = FALSE, colnames = c('Ensembl id' = 'id','Gene name' = 'name'),
        caption = title,
        extensions = 'Buttons', 
        options = list(
          dom = 'Bfrtip',
          buttons = c('copy', 'csv', 'excel', 'pdf', 'print') 
      ))
}

ExpressedTissues=2
lmat <- rbind( c(5,3,4), c(2,1,4) )
lhei <- c(0.2, 4)
lwid <- c(0.2, 4,0.1)
```

# Summary of applied parameters

<table>
<tbody>
<tr>
<td>
* Ensembl version: `r ENSEMBL_VER`
* Analysis conducted at `r analysis_level`
* RNA: 
   - quantification method: `r quantMethod`
   - Normalisation method: `r toupper(normMethod)`
* Protein: quantification method: <b> `r toupper(protQuant)`</b>
* 
```{r summaryProtGene, echo=FALSE, results='asis'}  
if(proteinCodingOnly){
  cat("Only 'protein coding' biotype kept")
}else{
  cat("All types of biotypes are kept")
}
```
</td>
<td>
*
```{r summaryMitoch,echo=FALSE, results='asis'}  
if(removeMitoch){
  cat("Mitochondria are REMOVED")
}else{
  cat("Mitochondria are kept")
}
```
* Correlation method in use: `r simpleCap(corrMethod)`
* 
```{r summaryCutoff, echo=FALSE, results='asis'}  
if(cutoff==0){
  cat(paste("Analyses include genes for which the mRNA is observed above 0",toupper(normMethod)))
}else{
  if(cutoff>0){
    cat(paste("Analyses include genes for which the mRNA is observed at least at",cutoff,toupper(normMethod)))
  }else{
    cat(paste("Invalid cutoff of expression"))
    flag4rChunks<-FALSE
    flag4rChunks2D<-FALSE
    flag4rChunks3D<-FALSE
  }
}
```
* 
```{r summaryCutoffprot, echo=FALSE, results='asis'}  
if(cutoffprot==0){
  cat(paste("Analyses include genes for which the protein is observed above 0"))
}else{
  if(cutoffprot>0){
    cat(paste("Analyses include genes for which the protein is observed at least at",cutoffprot))
  }else{
    cat(paste("Invalid cutoff of expression"))
    flag4rChunks<-FALSE
    flag4rChunks2D<-FALSE
    flag4rChunks3D<-FALSE
  }
}
```
* Log2-scalling applied to the data: `r log2scaling`
*
```{r summaryremoveNull, echo=FALSE, results='asis'}  
if(remove0){
  cat("Null values have been removed when possible")
}else{
  cat("Null values have been kept.")
}
```
</td>
</tr>
</tbody>
</table>

```{r noData2analyse,echo=!flag4rChunks,eval=!flag4rChunks,results='asis'}
cat("<h3 style='color: red; font-weight: bold;'>No result can be computed for the current combination of parameters.</h3>")
```

```{r loadDataHeaders,echo=flag4rChunks,eval=flag4rChunks,results='asis'}
cat("\n# Data Preparation")
```

```{r loadData, echo=flag4rChunks,eval=flag4rChunks,results='asis'}
DF1<-loadprotDF(labelDF1)
if(!cutoffprot==0) DF1<-strip(DF1,'ge',cutoffprot)

DF2<-loadRnaDF(labelDF2)
if(!cutoff==0) DF2<-strip(DF2,'ge',cutoff)
if(compDF=="3DF"){
  DF3<-loadRnaDF(labelDF3)
  if(!cutoff==0) DF3<-strip(DF3,'ge',cutoff)
}

if(proteinCodingOnly){
  DF2<-strip(filtre.dataset(DF2,g.Pcoding))
  if(compDF=="3DF")  DF3<-strip(filtre.dataset(DF3,g.Pcoding))
} 

if(log2scaling){
  DF1<-log2(DF1+pseudocount)
  DF2<-log2(DF2+pseudocount)
  
  if(compDF=="3DF") DF3<-log2(DF3+pseudocount)
}

```


```{r dataPrepTHeaders,results='asis', echo=flag4rChunks,eval=flag4rChunks}
cat("## Tissue filtering")
```

```{r dataPrepT, echo=flag4rChunks,eval=flag4rChunks,results='asis'}
if(compDF=="3DF"){
DrawVenn(fontfamily='Linux Libertine',
         cat.fontfamily='Linux Libertine',
     a=DF1,
     b=DF2,
     c=DF3,
     names=nameDFs,
     cols=datasetCol[nameDFs],
     type='colnames',
     cat.cex=rep(2,3),
     cat.dist=c(0.08,0.07,0.07),
     cex=rep(2,7),
     euler.d=FALSE,
     scaled=FALSE)
}else{
  if(compDF=="2DF"){
     DrawVenn(fontfamily='Linux Libertine',
              cat.fontfamily='Linux Libertine',
     a=DF1,
     b=DF2,
     names=nameDFs,
     cols=datasetCol[nameDFs],
     type='colnames',
     cat.cex=rep(2,2),
     cat.dist=c(0.07,0.03),
     cat.pos=c(330,45),
     cex=rep(2,3)
     )
  }
}


if(compDF=="2DF"){
    commonT<-Intersect(colnames(DF1),colnames(DF2))
    DF1<-strip(DF1[,commonT])
    DF2<-strip(DF2[,commonT])
}

if(compDF=="3DF"){
  commonT<-Intersect(colnames(DF1),colnames(DF2),colnames(DF3))
  DF1<-strip(DF1[,commonT])
  DF2<-strip(DF2[,commonT])
  DF3<-strip(DF3[,commonT])
  }

cat(paste('There are',length(commonT), 'common tissues between the datasets:'),commonT)
```


```{r dataPrepGHeaders,results='asis', echo=flag4rChunks,eval=flag4rChunks}
cat("## Gene filtering")
```

```{r unmatchedProtQ1,results='asis', echo=flag4rChunks,eval=flag4rChunks}
if(compDF=="3DF"){
  DrawVenn(fontfamily='Linux Libertine',
           cat.fontfamily='Linux Libertine',
     a=DF1,
     b=DF2,
     c=DF3,
     names=nameDFs,
     cols=datasetCol[nameDFs],
     type='rownames',
     cat.cex=rep(2,3),
     cat.dist=c(0.08,0.07,0.06),
     cex=rep(2,7),
     euler.d=FALSE,
     scaled=FALSE)
}else{
  if(compDF=="2DF"){
     DrawVenn(fontfamily='Linux Libertine',
              cat.fontfamily='Linux Libertine',
     a=DF1,
     b=DF2,
     names=nameDFs,
     cols=datasetCol[nameDFs],
     type='rownames',
     cat.cex=rep(2,2),
     cat.dist=c(0.07,0.03),
     cat.pos=c(330,45),
     cex=rep(2,3)
     )
  }
}

cat("\n### List of proteins not found as mRNAs\n")

if(compDF=="3DF"){
  unmatchedProt<-setdiff(rownames(DF1),union(rownames(DF2),rownames(DF3)))
}else{
  unmatchedProt<-setdiff(rownames(DF1),rownames(DF2))
}

geneID2df(unmatchedProt,title="Proteins unmatched by RNA (with the selected filters)")
```

```{r dataPrepG, echo=flag4rChunks,eval=flag4rChunks,results='asis'}
if(compDF=="3DF"){
  common.genes<-Intersect(rownames(DF1),rownames(DF2),rownames(DF3))
  DF1<-DF1[common.genes,]
  DF2<-DF2[common.genes,]
  DF3<-DF3[common.genes,]
}else{
  if(compDF=="2DF"){
    common.genes<-Intersect(rownames(DF1),rownames(DF2))
    DF1<-DF1[common.genes,]
    DF2<-DF2[common.genes,]
  }
}

cat(paste('There are',length(common.genes), 'common genes between the datasets.\n'))

if(removeMitoch) {
  DF1<-excludeGenes(DF1,mitoch)
  DF2<-excludeGenes(DF2,mitoch)
  if(compDF=="3DF") DF3<-excludeGenes(DF3,mitoch)
  
  cat(paste('As mitochondrial genes have been removed, analyses includes',nrow(DF1),'genes.\n'))
}
nameInit<-nameDFs
if(log2scaling){
  if(pseudocount){
    nameInit<-nameDFs
    nameDFs<-sapply(nameDFs,function(x) paste0('log2(',x,'+',pseudocount,')'))
    names(datasetCol)<-sapply(names(datasetCol),function(x) paste0('log2(',x,'+',pseudocount,')'))
    
    labelDF1<-paste0(labelDF1,'_log2_',pseudocount)
    labelDF2<-paste0(labelDF2,'_log2_',pseudocount)
    if(compDF=="3DF") labelDF3<-paste0(labelDF3,'_log2_',pseudocount)
  }else{
    nameInit<-nameDFs
    nameDFs<-sapply(nameDFs,function(x) paste0('log2(',x,')'))
    labelDF1<-paste0(labelDF1,'_log2')
    labelDF2<-paste0(labelDF2,'_log2')
    if(compDF=="3DF") labelDF3<-paste0(labelDF3,'_log2')
  }
}
```


# Tissue centric analyses

```{r TissueCor2DF, echo=flag4rChunks2D,eval=flag4rChunks2D,results='asis',warning=FALSE,message=FALSE}
cat("## Correlation \n")
corrMatDF1DF2<-compute_tissue_corr_matrix(DF1,DF2,labelDF1,labelDF2,method= corrMethod,report=FALSE)
cat("\n### Welch's t test\n")

cortTestDF1DF2<-t_test.CorrMat_identical.vs.different(corrMatDF1DF2,
                                                      labelDF1,labelDF2,
                                                      report=FALSE,
                                                      output='test')

cat("\n### Table\n")

pDF(corrMatDF1DF2,
    caption=paste(simpleCap(corrMethod),"correlation between",nameDFs[1],'and',nameDFs[2]))

cat("\n### Heatmap\n")
cat("\n#### with clustering\n")

heatmapWithClustering(corrMatDF1DF2,
                      label.A=nameDFs[1],label.B=nameDFs[2],
                      out.A=nameDFs[1], out.B=nameDFs[2],
                      dend='both',
                      margins=c(8,13),key.title=NA,key.xlab=paste(simpleCap(corrMethod),'correlation'),
                      key.ylab=NA,family='Linux Libertine',srtCol=45)

cat("\n#### ordered alphabetically \n")
heatmapAlphabet(corrMatDF1DF2,
                label.A=nameDFs[1],label.B=nameDFs[2],
                out.A=nameDFs[1], out.B=nameDFs[2],
                margins=c(9,10),key.title=NA,
                key.xlab=paste(simpleCap(corrMethod),'correlation'),
                key.ylab=NA,family='Linux Libertine',digits = 2,srtCol=45)
```


```{r TissueCor3DF, echo=flag4rChunks3D,eval=flag4rChunks3D,results='asis',warning=FALSE,message=FALSE}
cat("## Correlation {.tabset} \n")

cat(paste("### Between",nameDFs[1],'and',nameDFs[2],'\n'))

corrMatDF1DF2<-compute_tissue_corr_matrix(DF1,DF2,labelDF1,labelDF2,method= corrMethod,report=FALSE)
cat("\n#### Welch's t test\n")

cortTestDF1DF2<-t_test.CorrMat_identical.vs.different(corrMatDF1DF2,
                                                      labelDF1,labelDF2,
                                                      report=FALSE,
                                                      output='test')

cat("\n#### Table\n")

pDF(corrMatDF1DF2,
    caption=paste(simpleCap(corrMethod),"correlation between",nameDFs[1],'and',nameDFs[2]))

cat("\n#### Heatmap\n")
cat("\n##### with clustering\n")

heatmapWithClustering(corrMatDF1DF2,
                      label.A=nameDFs[1],label.B=nameDFs[2],
                      out.A=nameDFs[1], out.B=nameDFs[2],
                      dend='both',
                      margins=c(8,13),key.title=NA,key.xlab=paste(simpleCap(corrMethod),'correlation'),
                      key.ylab=NA,family='Linux Libertine',srtCol=45)

cat("\n#### ordered alphabetically \n")
heatmapAlphabet(corrMatDF1DF2,
                label.A=nameDFs[1],label.B=nameDFs[2],
                out.A=nameDFs[1], out.B=nameDFs[2],
                margins=c(9,10),key.title=NA,
                key.xlab=paste(simpleCap(corrMethod),'correlation'),
                key.ylab=NA,family='Linux Libertine',digits = 2,srtCol=45)

cat(paste("### Between",nameDFs[1],'and',nameDFs[3],"\n"))

corrMatDF1DF3<-compute_tissue_corr_matrix(DF1,DF3,labelDF1,labelDF3,method= corrMethod,report=FALSE)
cat("\n#### Welch's t test\n")

cortTestDF1DF3<-t_test.CorrMat_identical.vs.different(corrMatDF1DF3,
                                                      labelDF1,labelDF3,
                                                      report=FALSE,
                                                      output='test')

cat("\n#### Table\n")

pDF(corrMatDF1DF3,
    caption=paste(simpleCap(corrMethod),"correlation between",nameDFs[1],'and',nameDFs[3]))

cat("\n#### Heatmap\n")
cat("\n##### with clustering\n")

heatmapWithClustering(corrMatDF1DF3,
                      label.A=nameDFs[1],label.B=nameDFs[3],
                      out.A=nameDFs[1], out.B=nameDFs[3],
                      dend='both',
                      margins=c(8,13),key.title=NA,key.xlab=paste(simpleCap(corrMethod),'correlation'),
                      key.ylab=NA,family='Linux Libertine',srtCol=45)

cat("\n#### ordered alphabetically \n")
heatmapAlphabet(corrMatDF1DF3,
                label.A=nameDFs[1],label.B=nameDFs[3],
                out.A=nameDFs[1], out.B=nameDFs[3],
                margins=c(9,10),key.title=NA,
                key.xlab=paste(simpleCap(corrMethod),'correlation'),
                key.ylab=NA,family='Linux Libertine',digits = 2,srtCol=45)


cat(paste("### Between",nameDFs[2],'and',nameDFs[3],"\n"))

corrMatDF2DF3<-compute_tissue_corr_matrix(DF2,DF3,labelDF2,labelDF3,method= corrMethod,report=FALSE)
cat("\n#### Welch's t test\n")

cortTestDF2DF3<-t_test.CorrMat_identical.vs.different(corrMatDF2DF3,
                                                      labelDF2,labelDF3,
                                                      report=FALSE,
                                                      output='test')

cat("\n#### Table\n")

pDF(corrMatDF2DF3,
    caption=paste(simpleCap(corrMethod),"correlation between",nameDFs[2],'and',nameDFs[3]))


cat("\n#### Heatmap\n")
cat("\n##### with clustering\n")

heatmapWithClustering(corrMatDF2DF3,
                      label.A=nameDFs[2],label.B=nameDFs[3],
                      out.A=nameDFs[2], out.B=nameDFs[3],
                      dend='both',
                      margins=c(8,13),key.title=NA,key.xlab=paste(simpleCap(corrMethod),'correlation'),
                      key.ylab=NA,family='Linux Libertine',srtCol=45)

cat("\n#### ordered alphabetically \n")
heatmapAlphabet(corrMatDF2DF3,
                label.A=nameDFs[2],label.B=nameDFs[3],
                out.A=nameDFs[2], out.B=nameDFs[3],
                margins=c(9,10),key.title=NA,
                key.xlab=paste(simpleCap(corrMethod),'correlation'),
                key.ylab=NA,family='Linux Libertine',digits = 2,srtCol=45)

```

```{r TissueNbSpeGenes2DF, echo=flag4rChunks2D,eval=flag4rChunks2D,results='asis',warning=FALSE,message=FALSE}
cat("\n## Expression breadth")
breadth.DF1<-plotUniq.distrib(DF1,omit.zero=remove0,base_family='Linux Libertine')
breadth.DF2<-plotUniq.distrib(DF2,omit.zero=remove0,base_family='Linux Libertine')

title1<-makeTitle(nameInit[1],quantM=protQuant,cutoffprot)
title2<-makeTitle(nameInit[2],quantM=normMethod,cutoff)

print(breadth.DF1+ggtitle(title1)+theme_bw(base_size=16)+labs(y='protein count'))
print(breadth.DF2+ggtitle(title2)+theme_bw(base_size=16)+labs(y='mRNA count'))

```

```{r TissueNbSpeGenesBar2DF, echo=flag4rChunks2D,eval=flag4rChunks2D}
tryCatch(bibarplotsDiversityCond(DF1,DF2,
                        label1=title1,
                        threshold2=cutoff,label2=title2,
                        colorpal=TissueCol,output = 'ratio',
                        base_family='Linux Libertine'),
         error = function(c){
           c$message <- paste0('Not enough data to show')
         })
```


```{r TissueNbSpeGenes3DF, echo=flag4rChunks3D,eval=flag4rChunks3D,results='asis',warning=FALSE,message=FALSE}
cat("\n## Expression breadth")
breadth.DF1<-plotUniq.distrib(DF1,omit.zero=remove0,base_family='Linux Libertine')
breadth.DF2<-plotUniq.distrib(DF2,omit.zero=remove0,base_family='Linux Libertine')
breadth.DF3<-plotUniq.distrib(DF3,omit.zero=remove0,base_family='Linux Libertine')

title1<-makeTitle(nameInit[1],quantM=protQuant,cutoffprot)
title2<-makeTitle(nameInit[2],quantM=normMethod,cutoff)
title3<-makeTitle(nameInit[3],quantM=normMethod,cutoff)

print(breadth.DF1+ggtitle(title1)+theme_bw(base_size=16)+labs(y='protein count'))
print(breadth.DF2+ggtitle(title2)+theme_bw(base_size=16)+labs(y='mRNA count'))
print(breadth.DF3+ggtitle(title3)+theme_bw(base_size=16)+labs(y='mRNA count'))
```

```{r TissueNbSpeGenesBar3DF, echo=flag4rChunks3D,eval=flag4rChunks3D}
tryCatch(bibarplotsDiversityCond(DF1,DF2,
                        label1=title1,
                        threshold2=cutoff,label2=title2,
                        colorpal=TissueCol,output = 'ratio',
                        base_family='Linux Libertine'),
         error = function(c){
           c$message <- paste0('Not enough data to show')
         })

tryCatch(bibarplotsDiversityCond(DF1,DF3,
                        label1=title1,
                        threshold2=cutoff,label2=title3,
                        colorpal=TissueCol,output = 'ratio',
                        base_family='Linux Libertine'),
         error = function(c){
        c$message <- paste0('Not enough data to show')
         })

```


```{r TissueSharedExpBreadth2DF, echo=flag4rChunks2D,eval=flag4rChunks2D}
cat("\n## Shared expression breadth")

tryCatch(List[sharedEB_DF1DF2_DF1,sharedEB_DF1DF2_DF2,plotsharedEB_DF1DF2] <-cross.sharedDistrib(DF1,DF2,Lims=c(1,3,10,12)),
         error = function(c){
        c$message <- paste0('Not enough data to show')
         })
```



```{r TissueSharedExpBreadth3DF, echo=flag4rChunks3D,eval=flag4rChunks3D}
cat("\n### Shared expression breadth")

tryCatch(List[sharedEB_DF1DF2_DF1,sharedEB_DF1DF2_DF2,plotsharedEB_DF1DF2] <-cross.sharedDistrib(DF1,DF2,Lims=c(1,3,10,12)),
         error = function(c){
        c$message <- paste0('Not enough data to show')
         })

tryCatch(List[sharedEB_DF1DF3_DF1,sharedEB_DF1DF3_DF3,plotsharedEB_DF1DF3] <-cross.sharedDistrib(DF1,DF3,Lims=c(1,3,10,12)),
         error = function(c){
        c$message <- paste0('Not enough data to show')
         })
```

```{r TissueTS2DF, echo=flag4rChunks2D,eval=flag4rChunks2D, results='asis',warning=FALSE,message=FALSE}
cat("## Tissue specific genes: TS proteins and TS mRNAs (fold change method) \n")

overRatio.DF1DF2<-overlapSpeProtmRNA(DFprot=DF1,DFmRNA = DF2,pvalue = FALSE)
overRatioPval.DF1DF2<-overlapSpeProtmRNA(DFprot=DF1,DFmRNA = DF2,pvalue = TRUE)

heatmapAlphabet(t(overRatio.DF1DF2),
                label.A=title1,
                label.B=title2,
                margins=c(7,7),
                report=FALSE,key=FALSE,
                digits=2,cex.axis=5,
                annot='complete',sorting=FALSE,
                family='Linux Libertine',notecol="black",
                lmat=lmat,lhei=lhei,lwid=lwid,
                mathMethod = 'round')

heatmapAlphabet(t(overRatioPval.DF1DF2),
                label.A=title1,
                label.B=title2,
                margins=c(7,7),
                report=FALSE,key=FALSE,
                digits=2,cex.axis=5,
                annot='complete',sorting=FALSE,
                family='Linux Libertine',notecol="black",
                lmat=lmat,lhei=lhei,lwid=lwid,
                mathMethod = 'signif')


reportTmp<-t_test.Mat_identical.vs.different(overRatio.DF1DF2,xLab='Type',yLab='Jaccard Ind.',showMean=FALSE,pval=FALSE)
pander::pander(reportTmp)
reportTmp<-t_test.Mat_identical.vs.different(overRatioPval.DF1DF2,xLab='Type',yLab='p-values',showMean=FALSE,pval=FALSE)
pander::pander(reportTmp)

tmp<-lapply(setNames(commonT,commonT),
             function(x){
             cat(knitr::knit_print(geneID2df(overlapSpeProtmRNA(DFprot=DF1,
                         DFmRNA = DF2,
                         complete.matrix = FALSE,
                         pvalue = FALSE,
                         ratio=1,
                         xprot=x,
                         figure=TRUE,
                   categories=nameInit[1:2],outputType="intersect"),
                   paste("TS genes confirmed by",title1,"and",title2,"for",x))
             ))})
```

```{r TissueTS3DF, echo=flag4rChunks3D,eval=flag4rChunks3D, results='asis',warning=FALSE,message=FALSE}
cat("## Tissue specific genes: TS proteins and TS mRNAs (fold change method)\n")

cat(paste("\n### Between ",nameInit[1],"and",nameInit[2]))
overRatio.DF1DF2<-overlapSpeProtmRNA(DFprot=DF1,DFmRNA = DF2,pvalue = FALSE)
overRatioPval.DF1DF2<-overlapSpeProtmRNA(DFprot=DF1,DFmRNA = DF2,pvalue = TRUE)

heatmapAlphabet(t(overRatio.DF1DF2),
                label.A=title1,
                label.B=title2,
                margins=c(7,7),
                report=FALSE,key=FALSE,
                digits=2,cex.axis=5,
                annot='complete',sorting=FALSE,
                family='Linux Libertine',notecol="black",
                lmat=lmat,lhei=lhei,lwid=lwid,
                mathMethod = 'round')

heatmapAlphabet(t(overRatioPval.DF1DF2),
                label.A=title1,
                label.B=title2,
                margins=c(7,7),
                report=FALSE,key=FALSE,
                digits=2,cex.axis=5,
                annot='complete',sorting=FALSE,
                family='Linux Libertine',notecol="black",
                lmat=lmat,lhei=lhei,lwid=lwid,
                mathMethod = 'signif')


reportTmp<-t_test.Mat_identical.vs.different(overRatio.DF1DF2,xLab='Type',yLab='Jaccard Ind.',showMean=FALSE,pval=FALSE)
pander::pander(reportTmp)
reportTmp<-t_test.Mat_identical.vs.different(overRatioPval.DF1DF2,xLab='Type',yLab='p-values',showMean=FALSE,pval=FALSE)
pander::pander(reportTmp)

tmp<-lapply(setNames(commonT,commonT),
             function(x){
             cat(knitr::knit_print(geneID2df(overlapSpeProtmRNA(DFprot=DF1,
                         DFmRNA = DF2,
                         complete.matrix = FALSE,
                         pvalue = FALSE,
                         ratio=1,
                         xprot=x,
                         figure=TRUE,
                   categories=nameInit[1:2],outputType="intersect"),
                   paste("TS genes confirmed by",title1,"and",title2,"for",x))
             ))})

cat(paste("### Between ",nameInit[1],"and",nameInit[3]))
overRatio.DF1DF3<-overlapSpeProtmRNA(DFprot=DF1,DFmRNA = DF3,pvalue = FALSE)
overRatioPval.DF1DF3<-overlapSpeProtmRNA(DFprot=DF1,DFmRNA = DF3,pvalue = TRUE)

heatmapAlphabet(t(overRatio.DF1DF3),
                label.A=title1,
                label.B=title3,
                margins=c(7,7),
                report=FALSE,key=FALSE,
                digits=2,cex.axis=5,
                annot='complete',sorting=FALSE,
                family='Linux Libertine',notecol="black",
                lmat=lmat,lhei=lhei,lwid=lwid,
                mathMethod = 'round')

heatmapAlphabet(t(overRatioPval.DF1DF3),
                label.A=title1,
                label.B=title3,
                margins=c(7,7),
                report=FALSE,key=FALSE,
                digits=2,cex.axis=5,
                annot='complete',sorting=FALSE,
                family='Linux Libertine',notecol="black",
                lmat=lmat,lhei=lhei,lwid=lwid,
                mathMethod = 'signif')



reportTmp<-t_test.Mat_identical.vs.different(overRatio.DF1DF3,xLab='Type',yLab='Jaccard Ind.',showMean=FALSE,pval=FALSE)
pander::pander(reportTmp)
reportTmp<-t_test.Mat_identical.vs.different(overRatioPval.DF1DF3,xLab='Type',yLab='p-values',showMean=FALSE,pval=FALSE)
pander::pander(reportTmp)


tmp<-lapply(setNames(commonT,commonT),
             function(x){
             cat(knitr::knit_print(geneID2df(overlapSpeProtmRNA(DFprot=DF1,
                         DFmRNA = DF3,
                         complete.matrix = FALSE,
                         pvalue = FALSE,
                         ratio=1,
                         xprot=x,
                         figure=TRUE,
                   categories=nameInit[1:2],outputType="intersect"),
                   paste("TS genes confirmed by",title1,"and",title3,"for",x))
             ))})
```

## Trees 

Note: ExpressedTissues = `r ExpressedTissues`

```{r TissueTree2DF, echo=flag4rChunks2D,eval=flag4rChunks2D, results='asis',warning=FALSE,message=FALSE}
DF1.Bool<-computeBreadth(DF1, threshold=cutoffprot,omit.zero=TRUE,typeR='dfBool')
DF1.TM<-tissuesDistance(DF1.Bool,nbOfTissues=ExpressedTissues,plot=TRUE,method='ward.D')
plot(extractDendroTissueDistance(DF1.TM,plot=FALSE),'cladogram')

DF2.Bool<-computeBreadth(DF2, threshold=cutoffprot,omit.zero=TRUE,typeR='dfBool')
DF2.TM<-tissuesDistance(DF2.Bool,nbOfTissues=ExpressedTissues,plot=TRUE,method='ward.D') 
plot(extractDendroTissueDistance(DF2.TM,plot=FALSE),'cladogram')


consensus2D<-ape::consensus(list(extractDendroTissueDistance(DF1.TM,plot=FALSE),
                            extractDendroTissueDistance(DF2.TM,plot=FALSE)))
plot(consensus2D,'cladogram')
```


```{r TissueTree3DF, echo=flag4rChunks3D,eval=flag4rChunks3D, results='asis',warning=FALSE,message=FALSE}
DF1.Bool<-computeBreadth(DF1, threshold=cutoffprot,omit.zero=TRUE,typeR='dfBool')
DF1.TM<-tissuesDistance(DF1.Bool,nbOfTissues=ExpressedTissues,plot=TRUE,method='ward.D')
plot(extractDendroTissueDistance(DF1.TM,plot=FALSE),'cladogram')

DF2.Bool<-computeBreadth(DF2, threshold=cutoffprot,omit.zero=TRUE,typeR='dfBool')
DF2.TM<-tissuesDistance(DF2.Bool,nbOfTissues=ExpressedTissues,plot=TRUE,method='ward.D')  
 plot(extractDendroTissueDistance(DF2.TM,plot=FALSE),'cladogram')
           
DF3.Bool<-computeBreadth(DF3, threshold=cutoffprot,omit.zero=TRUE,typeR='dfBool')
DF3.TM<-tissuesDistance(DF3.Bool,nbOfTissues=ExpressedTissues,plot=TRUE,method='ward.D')
plot(extractDendroTissueDistance(DF3.TM,plot=FALSE),'cladogram')

consensus2D_DF2<-ape::consensus(list(extractDendroTissueDistance(DF1.TM,plot=FALSE),
                            extractDendroTissueDistance(DF2.TM,plot=FALSE)))
plot(consensus2D_DF2,'cladogram')


consensus2D_DF3<-ape::consensus(list(extractDendroTissueDistance(DF1.TM,plot=FALSE),
                            extractDendroTissueDistance(DF3.TM,plot=FALSE)))
plot(consensus2D_DF3,'cladogram')

consensus3D<-ape::consensus(list(extractDendroTissueDistance(DF1.TM,plot=FALSE),
                            extractDendroTissueDistance(DF2.TM,plot=FALSE),
                            extractDendroTissueDistance(DF3.TM,plot=FALSE)))
plot(consensus3D,'cladogram')
```

